Morality, politics, and cooperation

### 2021-12-16 manuscript/manuscript.Rmd
just omit the scale that prevents convergence. add meta-analysis

```{r setup, include=FALSE}
# We recommend that you prepare your raw data for analysis in 'prepare_data.R',
# and end that file with either open_data(yourdata), or closed_data(yourdata).
# Then, uncomment the line below to load the original or synthetic data
# (whichever is available), to allow anyone to reproduce your code:
library("worcs")
knitr::opts_chunk$set(echo = FALSE, results = "hide", message = FALSE, warning = FALSE)
options(knitr.kable.NA = '')
library(ggplot2)
library(tidySEM)
library(lavaan)
library(semTools)
library(kableExtra)
library(bookdown)
library(psych)
dat <- load_data(to_envir = FALSE)[1:3]
source("../scales_list.R")
scales_list <- lapply(scales_list, function(i){
  tmp <- lapply(names(i), function(j){ paste0(j, "_", 1:length(i[[j]]))})
  names(tmp) <- names(i)
  tmp
  })
set.seed(1)
cfas <- lapply(names(scales_list), function(cnt){
  results <- t(sapply(scales_list[[cnt]], function(scal){
    out <- cfa(paste0("F =~ ", paste0(scal, collapse = "+")), std.lv = TRUE, data = dat[[cnt]])
    paran <- fa.parallel(dat[[cnt]][, scal])
    tab <- table_results(out, columns = NULL, digits=3)
    tab <- tab[-nrow(tab), ]
    loadns <- as.numeric(tab$est_std)[tab$op == "=~"]
    r2s <- lavInspect(out, "r2")
    omga <- semTools::reliability(out, what = "omega")[1,1]
    c(Subscale = gsub("_\\d$", "", scal[1]),
      Items = length(scal),
      n = out@Data@nobs[[1]],
      formatC(unlist(table_fit(out)[1, c("chisq", "cfi", "tli", "rmsea", "srmr")]), digits = 3, format = "f"), 
      formatC(c(min_load = min(loadns), max_load = max(loadns), min_r2 = min(r2s), max_r2 = max(r2s), omega = omga), digits = 3, format = "f"),
      Reliability = tidySEM:::interpret(omga),
      Factors = fa.parallel(dat[[cnt]][,scal]) $nfact
      )
  }))
})
names(cfas) <- names(scales_list)
```

@@

When attempting to conduct the preregistered analyses,
the model did not converge in one of the datasets (NL).
We examined individual CFAs for the included scales to determine potential
sources of misspecification.
These analyses, summarized below, indicated that several scales in that dataset
displayed evidence of not being unidimensional or had no factors with Eigenvalues greater than would be expected by random chance (see column 'Factors', which is based on Horn's parallel analysis, 1965),
had poor reliability (estimated using McDonald's Omega, which is calculated from the factor loadings and does not assume that all factor loadings are identical as Cronbach's alpha does).

@@

To understand these issues better, we performed exploratory factor analysis on scales that showed indications of being non-unidimensional in at least one country.

```{r notunidim, results = "asis"}
allscales <- do.call(c, scales_list)
nfacs <- as.integer(do.call(c, lapply(cfas, function(i){i[, 'Factors']})))
check_these <- nfacs > 1
these_scales <- unique(do.call(c, lapply(cfas, function(i){i[, 'Subscale']}))[check_these])
check_these <- grep(paste0("^.{2}\\.(", paste0(these_scales, collapse = "|"), ")$"), names(allscales))
these_scales <- allscales[check_these]
nfacs <- nfacs[check_these]
nfacs[nfacs == 0] <- 2
out <- mapply(function(scal, nfac){
  fa(dat[[substring(scal, first = 1, last = 2)]][these_scales[[scal]]], nfac)
}, scal = names(these_scales), nfac = rep(2, length(these_scales)))

@@

These factor analyses suggest that items 3-5 of sepa_soc loaded most consistently on the same factor.
Similarly, items 3-5 of sepa_eco loaded most consistently on the same factor.
For secs_soc, only items 4-5 loaded consistently high on the same factor.
For secs_eco, no items loaded consistently high on the same factor.
We removed items not consistently loading on one factor,
and dropped secs_eco entirely.
We applied these changes consistently across countries.

```{r, include=FALSE}
use_scales <- lapply(scales_list, function(i){
  thenames <- grepl("sepa_(soc|eco)", names(i))
  if(any(thenames)){
    i[which(thenames)] <- lapply(i[which(thenames)], `[`, 3:5)
  }
  i
})
use_scales <- lapply(use_scales, function(i){
  thenames <- grepl("secs_soc", names(i))
  if(any(thenames)){
    i[which(thenames)] <- lapply(i[which(thenames)], `[`, 4:5)
  }
  i
})
use_scales$us$secs_eco <- NULL
use_scales$nl$secs_eco <- NULL

set.seed(1)
cfas <- lapply(names(use_scales), function(cnt){
  results <- t(sapply(use_scales[[cnt]], function(scal){
    out <- cfa(paste0("F =~ ", paste0(scal, collapse = "+")), std.lv = TRUE, data = dat[[cnt]])
    paran <- fa.parallel(dat[[cnt]][, scal])
    tab <- table_results(out, columns = NULL, digits=3)
    tab <- tab[-nrow(tab), ]
    loadns <- as.numeric(tab$est_std)[tab$op == "=~"]
    r2s <- lavInspect(out, "r2")
    omga <- semTools::reliability(out, what = "omega")[1,1]
    c(Subscale = gsub("_\\d$", "", scal[1]),
      Items = length(scal),
      n = out@Data@nobs[[1]],
      formatC(unlist(table_fit(out)[1, c("chisq", "cfi", "tli", "rmsea", "srmr")]), digits = 3, format = "f"), 
      formatC(c(min_load = min(loadns), max_load = max(loadns), min_r2 = min(r2s), max_r2 = max(r2s), omega = omga), digits = 3, format = "f"),
      Reliability = tidySEM:::interpret(omga),
      Factors = invisible(fa.parallel(dat[[cnt]][,scal])$nfact)
      )
  }))
})
names(cfas) <- names(use_scales)

meas_inv <- sapply(use_scales$dk, function(scal){
  tmpdat <- rbind(tryCatch(cbind(dat$nl[, scal], Country = "NL"), error = function(e) NULL),
                  tryCatch(cbind(dat$dk[, scal], Country = "DK"), error = function(e) NULL),
                  tryCatch(cbind(dat$us[, scal], Country = "US"), error = function(e) NULL))
  conf <- cfa(paste0("F =~ ", paste0(scal, collapse = "+")), std.lv = TRUE, data = tmpdat, group = "Country")
  metr <- cfa(paste0("F =~ ", paste0(scal, collapse = "+")), std.lv = TRUE, data = tmpdat, group = "Country", group.equal = "loadings")
  tst <- anova(conf, metr)
  unlist(tst[2, c("Chisq diff", "Df diff", "Pr(>Chisq)")])
})
```

```{r tabscaleuse, results = "asis"}
invisible(lapply(names(cfas), function(cntr){
  print({kbl(cfas[[cntr]], caption = paste0("Scale reliability ", cntr)) |>
  kable_styling(bootstrap_options = c("striped", "hover"))
})}))
```

@@

```{r, code=xfun::read_utf8('../analysis.R')}

@@

```{r tabresults, results = "asis"}
interpret_bf <- function(bf){
  sapply(bf, function(bf){
    if(bf < 1/10) return("rejected")
    if(bf < 1/3) return("rejected")
    if(bf >= 1/3 & bf <= 3) return("inconclusive")
    if(bf > 3 & bf <= 10) return("supported")
  return("supported")
  })
}
invisible(lapply(1:length(bayesfactors), function(h){
  print({
    kbl(est_for_hyp[[h]], caption = paste0("Parameters used to test hypothesis ", h, ". Evidence in favor of the hypothesis: BF = ", formatC(bayesfactors[h], digits = 3, format = "f"), " (", interpret_bf(bayesfactors[h]), ")."), digits = 3) |>
  kable_styling(bootstrap_options = c("striped", "hover"))
})}))
```

@@

>>>>

```{r setup, include=FALSE}
# We recommend that you prepare your raw data for analysis in 'prepare_data.R',
# and end that file with either open_data(yourdata), or closed_data(yourdata).
# Then, uncomment the line below to load the original or synthetic data
# (whichever is available), to allow anyone to reproduce your code:
library("worcs")
run_everything = FALSE
knitr::opts_chunk$set(echo = FALSE, results = "hide", message = FALSE, warning = FALSE)
options(knitr.kable.NA = '')
library(ggplot2)
library(tidySEM)
library(lavaan)
library(semTools)
library(kableExtra)
library(bookdown)
library(psych)
library(knitr)
dat <- load_data(to_envir = FALSE)[1:3]
source("../scales_list.R")
scales_list <- lapply(scales_list, function(i){
  tmp <- lapply(names(i), function(j){ paste0(j, "_", 1:length(i[[j]]))})
  names(tmp) <- names(i)
  tmp
  })
```

```{r cfas, eval = run_everything}
set.seed(1)
cfas <- lapply(names(scales_list), function(cnt){
  results <- t(sapply(scales_list[[cnt]], function(scal){
    out <- cfa(paste0("F =~ ", paste0(scal, collapse = "+")), std.lv = TRUE, data = dat[[cnt]])
    paran <- fa.parallel(dat[[cnt]][, scal])
    tab <- table_results(out, columns = NULL, digits=3)
    tab <- tab[-nrow(tab), ]
    loadns <- as.numeric(tab$est_std)[tab$op == "=~"]
    r2s <- lavInspect(out, "r2")
    omga <- semTools::reliability(out, what = "omega")[1,1]
    c(Subscale = gsub("_\\d$", "", scal[1]),
      Items = length(scal),
      n = out@Data@nobs[[1]],
      formatC(unlist(table_fit(out)[1, c("chisq", "cfi", "tli", "rmsea", "srmr")]), digits = 3, format = "f"), 
      formatC(c(min_load = min(loadns), max_load = max(loadns), min_r2 = min(r2s), max_r2 = max(r2s), omega = omga), digits = 3, format = "f"),
      Reliability = tidySEM:::interpret(omga),
      Factors = fa.parallel(dat[[cnt]][,scal]) $nfact
      )
  }))
})
names(cfas) <- names(scales_list)
saveRDS(cfas, "cfas.RData")
```
```{r}
cfas <- readRDS("cfas.RData")
```

@@

When attempting to conduct the preregistered analyses,
the model did not converge in one of the datasets (NL).
We examined individual CFAs for the included scales to determine potential
sources of misspecification.
These analyses indicated that the scale `secs_eco` in that dataset
had no factors with Eigenvalues greater than would be expected by random chance (see column 'Factors', which is based on Horn's parallel analysis, 1965),
and had poor reliability (estimated using McDonald's Omega, which is calculated from the factor loadings and does not assume that all factor loadings are identical as Cronbach's alpha does).
After deleting this scale, the CFA model converged.
It was therefore deemed necessary to remove this scale.

@@

<!-- To understand these issues better, we performed exploratory factor analysis on scales that showed indications of being non-unidimensional in at least one country. -->

```{r notunidim, results = "asis", include = FALSE}
allscales <- do.call(c, scales_list)
nfacs <- as.integer(do.call(c, lapply(cfas, function(i){i[, 'Factors']})))
check_these <- nfacs > 1
these_scales <- unique(do.call(c, lapply(cfas, function(i){i[, 'Subscale']}))[check_these])
check_these <- grep(paste0("^.{2}\\.(", paste0(these_scales, collapse = "|"), ")$"), names(allscales))
these_scales <- allscales[check_these]
nfacs <- nfacs[check_these]
nfacs[nfacs == 0] <- 2
out <- mapply(function(scal, nfac){
  fa(dat[[substring(scal, first = 1, last = 2)]][these_scales[[scal]]], nfac)
}, scal = names(these_scales), nfac = rep(2, length(these_scales)))

@@

<!-- These factor analyses suggest that items 3-5 of sepa_soc loaded most consistently on the same factor. -->
<!-- Similarly, items 1-3 of sepa_eco loaded most consistently on the same factor. -->
<!-- For secs_soc, only items 4-5 loaded consistently high on the same factor. -->
<!-- For secs_eco, no items loaded consistently high on the same factor. -->
<!-- We removed items not consistently loading on one factor, -->
<!-- and dropped secs_eco entirely. -->
<!-- We applied these changes consistently across countries. -->

```{r, include=FALSE}
use_scales <- scales_list
use_scales$nl$secs_eco <- NULL
```

```{r, eval = run_everything}
set.seed(1)
cfas <- lapply(names(use_scales), function(cnt){
  results <- t(sapply(use_scales[[cnt]], function(scal){
    out <- cfa(paste0("F =~ ", paste0(scal, collapse = "+")), std.lv = TRUE, data = dat[[cnt]])
    paran <- fa.parallel(dat[[cnt]][, scal])
    tab <- table_results(out, columns = NULL, digits=3)
    tab <- tab[-nrow(tab), ]
    loadns <- as.numeric(tab$est_std)[tab$op == "=~"]
    r2s <- lavInspect(out, "r2")
    omga <- semTools::reliability(out, what = "omega")[1,1]
    c(Subscale = gsub("_\\d$", "", scal[1]),
      Items = length(scal),
      n = out@Data@nobs[[1]],
      formatC(unlist(table_fit(out)[1, c("chisq", "cfi", "tli", "rmsea", "srmr")]), digits = 3, format = "f"), 
      formatC(c(min_load = min(loadns), max_load = max(loadns), min_r2 = min(r2s), max_r2 = max(r2s), omega = omga), digits = 3, format = "f"),
      Reliability = tidySEM:::interpret(omga),
      Factors = invisible(fa.parallel(dat[[cnt]][,scal])$nfact)
      )
  }))
})
names(cfas) <- names(use_scales)

meas_inv <- sapply(use_scales$dk, function(scal){
  tmpdat <- rbind(tryCatch(cbind(dat$nl[, scal], Country = "NL"), error = function(e) NULL),
                  tryCatch(cbind(dat$dk[, scal], Country = "DK"), error = function(e) NULL),
                  tryCatch(cbind(dat$us[, scal], Country = "US"), error = function(e) NULL))
  conf <- cfa(paste0("F =~ ", paste0(scal, collapse = "+")), std.lv = TRUE, data = tmpdat, group = "Country")
  metr <- cfa(paste0("F =~ ", paste0(scal, collapse = "+")), std.lv = TRUE, data = tmpdat, group = "Country", group.equal = "loadings")
  tst <- anova(conf, metr)
  unlist(tst[2, c("Chisq diff", "Df diff", "Pr(>Chisq)")])
})
saveRDS(cfas, "cfas2.RData")
saveRDS(meas_inv, "meas_inv.RData")
```

```{r tabscaleuse, results = "asis"}
cfas <- readRDS("cfas2.RData")
meas_inv <- readRDS("meas_inv.RData")
invisible(lapply(names(cfas), function(cntr){
  print({kbl(cfas[[cntr]], caption = paste0("Scale reliability ", cntr)) |>
  kable_styling(bootstrap_options = c("striped", "hover"))
})}))
```

@@

```{r, eval = run_everything}
library(worcs)
library(lavaan)
library(BFpack)
library(ggplot2)
library(tidySEM)
library(metafor)
set.seed(22)
sample_sizes <- sapply(dat, nrow)
hypotheses <- list("(fam_secs_soc_us, fam_secs_eco_us, fam_sepa_soc_dk, fam_sepa_eco_dk, fam_secs_soc_nl, fam_secs_eco_nl, fam_sepa_soc_nl, fam_sepa_eco_nl) > .1",
                   "(grp_secs_soc_us, grp_secs_eco_us, grp_sepa_soc_dk, grp_sepa_eco_dk, grp_secs_soc_nl, grp_secs_eco_nl, grp_sepa_soc_nl, grp_sepa_eco_nl) > .1",
                   "(rec_secs_soc_us, rec_secs_eco_us, rec_sepa_soc_dk, rec_sepa_eco_dk, rec_secs_soc_nl, rec_secs_eco_nl, rec_sepa_soc_nl, rec_sepa_eco_nl) > .1",
                   "(her_secs_soc_us, her_secs_eco_us, her_sepa_soc_dk, her_sepa_eco_dk, her_secs_soc_nl, her_secs_eco_nl, her_sepa_soc_nl, her_sepa_eco_nl) > .1",
                   "(def_secs_soc_us, def_secs_eco_us, def_sepa_soc_dk, def_sepa_eco_dk, def_secs_soc_nl, def_secs_eco_nl, def_sepa_soc_nl, def_sepa_eco_nl) > .1",
                   "(fai_secs_soc_us, fai_secs_eco_us, fai_sepa_soc_dk, fai_sepa_eco_dk, fai_secs_soc_nl, fai_secs_eco_nl, fai_sepa_soc_nl, fai_sepa_eco_nl) < -.1",
                   "(pro_secs_soc_us, pro_secs_eco_us, pro_sepa_soc_dk, pro_sepa_eco_dk, pro_secs_soc_nl, pro_secs_eco_nl, pro_sepa_soc_nl, pro_sepa_eco_nl) > .1"
                   )
hypotheses[[8]] <- gsub("[<>]", "=", gsub("\\b(fam|grp)_((sepa|secs)_(soc|eco))_", "\\2ON\\1_", gsub("\\) > 0 & \\(", ", ", paste0(gsub("-?\\.1", "0", hypotheses[[1]]), " & ", gsub(".1", "0", hypotheses[[2]], fixed = TRUE)))))
hypotheses[[9]] <- gsub("fam", "rec", gsub("grp", "fai", hypotheses[[8]], fixed = TRUE), fixed = TRUE)

mods_cor <- lapply(names(dat), function(country){
  cntdat <- dat[[country]][unlist(use_scales[[country]])]
  mod <- tidy_sem(cntdat)
  measurement(mod)
})
names(mods_cor) <- names(dat)
mods_8 <- lapply(mods_cor, function(x){
  add_paths(x,   paste0((t(outer(paste0(unique(grep("^se", x$dictionary$scale, value = TRUE)), " ~ "),
                                 unique(grep("^(fam|grp)", x$dictionary$scale, value = TRUE)), paste0))), collapse = "\n"))
})
mods_9 <- lapply(mods_cor, function(x){
  add_paths(x,   paste0((t(outer(paste0(unique(grep("^se", x$dictionary$scale, value = TRUE)), " ~ "),
                                 unique(grep("^(rec|fai)", x$dictionary$scale, value = TRUE)), paste0))), collapse = "\n"))
})

removeothercountries <- function(hyp, cnt){
  gsub(",\\s+\\)", "\\)", gsub(paste0("\\b[a-zA-Z_]+(?<!", cnt, ")\\b,?"), "", hyp, perl = TRUE))
}

removeparameters <- function(hyp, est){
  params_in_hyp <- bain:::params_in_hyp(hyp)
  est <- names(est)
  if(any(!params_in_hyp %in% est)){
    for(param in params_in_hyp[!params_in_hyp %in% est]){
      hyp <- gsub(paste0("\\b", param, "\\b,?"), "", hyp)
    }
    hyp <- gsub(",\\s+\\)", "\\)", hyp)
    hyp <- gsub("\\(\\s+", "\\(", hyp)
  }
  hyp <- gsub("\\(([a-zA-Z_]+)\\)", "\\1", hyp)
  if(length(bain:::params_in_hyp(hyp)) == 0) return(NA)
  hyp
}

res_list <- lapply(mods_cor, function(x){estimate_lavaan(x)})
res_list17 <- res_list
res <- lapply(names(res_list), function(country){
  thisfit = res_list[[country]]
  tab <- bain:::lav_get_estimates(thisfit, standardize = TRUE, retain_which = "~~")
  keep_these <- which(!grepl("~~(secs|sepa)_(soc|eco)$", names(tab$estimate)) & grepl("(secs|sepa)_(soc|eco)~~", names(tab$estimate)))
  estimates <- tab$estimate[keep_these]
  Sigma <- tab$Sigma[[1]][keep_these, keep_these]
  names(estimates) <- paste0(gsub("~~", "_", names(estimates), fixed = TRUE), "_", country)
  names(estimates) <- gsub("^(sepa|secs)_(.+?)_(.+?)_(.+)$", "\\3_\\1_\\2_\\4", names(estimates))
  colnames(Sigma) <- rownames(Sigma) <- names(estimates)
  list(est = estimates, sig = Sigma)
})
names(res) <- names(res_list)
res_h17 <- res
# Get individual BFs for each sample
bf_individual <- sapply(1:length(res_list), function(i){
  hyp <- paste2(unlist(
    lapply(
      lapply(hypotheses[1:7], removeothercountries, cnt = names(res_list)[i]),
      removeparameters, est = res[[i]]$est)
    ), collapse = "; ")
  tmp <- BF(x = res[[i]]$est,
            hypothesis = hyp,
            Sigma = res[[i]]$sig,
            n = sample_sizes[i])
  tmp$BFtu_confirmatory[1:7]
})
out_cors <- apply(bf_individual, 1, prod)

out_8 <- 
  {
    # fit model
    res_list <- lapply(mods_8, function(x){estimate_lavaan(x)})
    res_list8 <- res_list
    res <- lapply(names(res_list), function(country){
      thisfit = res_list[[country]]
      tab <- bain:::lav_get_estimates(thisfit, standardize = TRUE, retain_which = "~")
      estimates <- tab$estimate
      Sigma <- tab$Sigma[[1]]
      names(estimates) <- paste0(gsub("~", "ON", names(estimates), fixed = TRUE), "_", country)
      colnames(Sigma) <- rownames(Sigma) <- names(estimates)
      list(est = estimates, sig = Sigma)
    })
    res8 <- res
    bf_individual8 <- sapply(1:length(res_list), function(i){
      hyp <- removeparameters(removeothercountries(hypotheses[8], cnt = names(res_list)[i]), est = res[[i]]$est)
      tmp <- BF(x = res[[i]]$est,
                hypothesis = hyp,
                Sigma = res[[i]]$sig,
                n = sample_sizes[i])
      tmp$BFtu_confirmatory[1]
    })
    prod(bf_individual8)
  }
out_9 <- 
  {
    # fit model
    res_list <- lapply(mods_9, function(x){estimate_lavaan(x)})
    res_list9 <- res_list
    res <- lapply(names(res_list), function(country){
      thisfit = res_list[[country]]
      tab <- bain:::lav_get_estimates(thisfit, standardize = TRUE, retain_which = "~")
      estimates <- tab$estimate
      Sigma <- tab$Sigma[[1]]
      names(estimates) <- paste0(gsub("~", "ON", names(estimates), fixed = TRUE), "_", country)
      colnames(Sigma) <- rownames(Sigma) <- names(estimates)
      list(est = estimates, sig = Sigma)
    })
    res9 <- res
    bf_individual9 <- sapply(1:length(res_list), function(i){
      hyp <- removeparameters(removeothercountries(hypotheses[9], cnt = names(res_list)[i]), est = res[[i]]$est)
      tmp <- BF(x = res[[i]]$est,
                hypothesis = hyp,
                Sigma = res[[i]]$sig,
                n = sample_sizes[i])
      tmp$BFtu_confirmatory[1]
    })
    prod(bf_individual9)
  }
bayesfactors <- c(out_cors, 1/out_8, 1/out_9)
est_for_hyp <- lapply(hypotheses, function(h){
  pars = bain:::params_in_hyp(h)
  tmp <- unlist(lapply(c(res_h17, res8, res9), function(i){
    i$est[which(names(i$est) %in% pars)]
  }))
  nams <- names(tmp)
  tmp <- data.frame(Value = tmp, Country = gsub("^.+(.{2})$", "\\1", nams), Parameter = gsub("^(.{2}\\.)?(.+?)_.{2}$", "\\2", nams))
  tmp <- reshape(tmp, direction = "wide", idvar = "Country", timevar =  "Parameter")
  rownames(tmp) <- NULL
  names(tmp) <- gsub("Value\\.", "", names(tmp))
  tmp
})

estimates <- lapply(names(res_list17), function(c){
    x <- res_list17[[c]]
    tmp <- standardizedSolution(x)
    tmp <- tmp[tmp$op == "~~" & grepl("(soc|eco)", tmp$lhs) & !grepl("(soc|eco)", tmp$rhs), c("rhs", "lhs", "est.std", "se")]
    names(tmp)[3] <- "ri"
    tmp$social <- as.integer(grepl("_soc", tmp$lhs, fixed = TRUE))
    tmp$eco <- as.integer(grepl("_eco", tmp$lhs, fixed = TRUE))
    tmp$country <- c
    tmp$ni <- unlist(x@Data@nobs)
    tmp
})
estimates <- do.call(rbind, estimates)

meta17 <- lapply(unique(estimates$rhs), function(x){
  tmp <- estimates[estimates$rhs==x,]
  tmp <- escalc(ri = tmp$ri, ni = tmp$ni, measure = "ZCOR", data = tmp)
  # res <- rma(tmp$yi, vi = tmp$vi, mods = tmp[, c("social", "eco")], intercept = FALSE)
  # if(length(unique(tmp$country))>2){
  #   res <- robust(res, cluster = tmp$country)  
  # }
  tmp$id_study <- tmp$country
  tmp$id_es <- 1:nrow(tmp)
  res <- rma.mv(tmp$yi, tmp$vi, random = list(~ 1 | id_study, ~ 1 | id_es), data=tmp) 
  confints <- confint(res)
  tabres <- data.frame(Parameter = c(rownames(res$b), "Tau2b", "Tau2w"),
                       Estimate = c(fisherz2r(res$b), res$sigma2),
                       ci.lb = c(fisherz2r(res$ci.lb), confints[[1]]$random[1,2], confints[[2]]$random[1,2]),
                       ci.ub = c(fisherz2r(res$ci.ub), confints[[1]]$random[1,3], confints[[2]]$random[1,3]),
                       p = c(res$pval, NA, NA),
                       sig = c(c("", "*")[(res$pval < .05)+1], c("", "*")[(c(confints[[1]]$random[1,2], confints[[2]]$random[1,2])> 1e-4)+1]),
                       Model = "Overall")
  # By conservatism dimension
  res <- rma.mv(tmp$yi, tmp$vi, random = list(~ 1 | id_study, ~ 1 | id_es), data=tmp, intercept = FALSE, mods = tmp[, c("social", "eco")]) 
  confints <- confint(res)
  tabres2 <- data.frame(Parameter = c(rownames(res$b), "Tau2b", "Tau2w"),
                       Estimate = c(fisherz2r(res$b), res$sigma2),
                       ci.lb = c(fisherz2r(res$ci.lb), confints[[1]]$random[1,2], confints[[2]]$random[1,2]),
                       ci.ub = c(fisherz2r(res$ci.ub), confints[[1]]$random[1,3], confints[[2]]$random[1,3]),
                       p = c(res$pval, NA, NA),
                       sig = c(c("", "*")[(res$pval < .05)+1], c("", "*")[(c(confints[[1]]$random[1,2], confints[[2]]$random[1,2])> 1e-4)+1]),
                       Model = "Multigroup")
  tabres <- rbind(tabres, tabres2)
  tabres$CI <- conf_int(lb = tabres$ci.lb, ub = tabres$ci.ub)
  tabres[c("ci.lb", "ci.ub")] <- NULL
  tabres$Domain <- x
  tabres
})
meta17 <- do.call(rbind, meta17)

# Hypothesis 8 ------------------------------------------------------------
source("mod89.R")
res8 <- lapply(names(mod8), function(n){
  sem(mod8[[n]], dat[[n]], auto.fix.first = FALSE, auto.var = TRUE, auto.cov.lv.x = TRUE, std.lv = TRUE, auto.cov.y = TRUE)
})
names(res8) <- names(mod8)

estimates <- lapply(names(res8), function(c){
  x <- res8[[c]]
  tmp <- parameterestimates(x)
  tmp <- tmp[!tmp$label == "", c("rhs", "lhs", "est", "se")]
  names(tmp)[3] <- "bi"
  tmp$social <- as.integer(grepl("_soc", tmp$lhs, fixed = TRUE))
  tmp$eco <- as.integer(grepl("_eco", tmp$lhs, fixed = TRUE))
  tmp$country <- c
  tmp$ni <- unlist(x@Data@nobs)
  tmp
})
estimates <- do.call(rbind, estimates)

meta8 <- lapply(c("fam", "grp"), function(x){
  tmp <- estimates[estimates$rhs==x,]
  tmp$id_study <- tmp$country
  tmp$id_es <- 1:nrow(tmp)
  if(nrow(tmp) == 1) return(NULL)
  res <- tryCatch({rma.mv(tmp$bi, tmp$se^2, random = list(~ 1 | id_study, ~ 1 | id_es), data=tmp) }, error = function(e){rma(tmp$bi, tmp$se^2, data=tmp)})
  confints <- confint(res)
  tabres <- data.frame(Parameter = c(rownames(res$b), "Tau2b", "Tau2w"),
                       Estimate = c(fisherz2r(res$b), res$sigma2),
                       ci.lb = c(fisherz2r(res$ci.lb), confints[[1]]$random[1,2], confints[[2]]$random[1,2]),
                       ci.ub = c(fisherz2r(res$ci.ub), confints[[1]]$random[1,3], confints[[2]]$random[1,3]),
                       p = c(res$pval, NA, NA),
                       sig = c(c("", "*")[(res$pval < .05)+1], c("", "*")[(c(confints[[1]]$random[1,2], confints[[2]]$random[1,2])> 1e-4)+1]),
                       Model = "Overall")
  # By conservatism dimension
  res <- try(rma.mv(tmp$bi, tmp$se^2, random = list(~ 1 | id_study, ~ 1 | id_es), data=tmp, intercept = FALSE, mods = tmp[, c("social", "eco")]))
  if(inherits(res, "try-error")) return(tabres)
  confints <- confint(res)
  tabres2 <- data.frame(Parameter = c(rownames(res$b), "Tau2b", "Tau2w"),
                        Estimate = c(fisherz2r(res$b), res$sigma2),
                        ci.lb = c(fisherz2r(res$ci.lb), confints[[1]]$random[1,2], confints[[2]]$random[1,2]),
                        ci.ub = c(fisherz2r(res$ci.ub), confints[[1]]$random[1,3], confints[[2]]$random[1,3]),
                        p = c(res$pval, NA, NA),
                        sig = c(c("", "*")[(res$pval < .05)+1], c("", "*")[(c(confints[[1]]$random[1,2], confints[[2]]$random[1,2])> 1e-4)+1]),
                        Model = "Multigroup")
  if(tabres$Estimate[1] == tabres2$Estimate[1]) return(tabres)
  tabres <- rbind(tabres, tabres2)
  tabres$CI <- conf_int(lb = tabres$ci.lb, ub = tabres$ci.ub)
  tabres[c("ci.lb", "ci.ub")] <- NULL
  tabres$Domain <- x
  tabres
})
meta8 <- do.call(rbind, meta8)

# Hypothesis 9 ------------------------------------------------------------

res9 <- lapply(names(mod8), function(n){
  mod <- mod8[[n]]
  mod <- gsub("secs_soc_fam", "secs_soc_rec", mod, fixed = T)
  mod <- gsub("secs_soc_grp", "secs_soc_fai", mod, fixed = T)
  mod <- gsub("* fam", "* rec", mod, fixed = T)
  mod <- gsub("* grp", "* fai", mod, fixed = T)
  sem(mod, dat[[n]], auto.fix.first = FALSE, auto.var = TRUE, auto.cov.lv.x = TRUE, std.lv = TRUE, auto.cov.y = TRUE)
})
names(res9) <- names(mod8)

estimates <- lapply(names(res9), function(c){
  x <- res9[[c]]
  tmp <- parameterestimates(x)
  tmp <- tmp[!tmp$label == "", c("rhs", "lhs", "est", "se")]
  names(tmp)[3] <- "bi"
  tmp$social <- as.integer(grepl("_soc", tmp$lhs, fixed = TRUE))
  tmp$eco <- as.integer(grepl("_eco", tmp$lhs, fixed = TRUE))
  tmp$country <- c
  tmp$ni <- unlist(x@Data@nobs)
  tmp
})
estimates <- do.call(rbind, estimates)

meta9 <- lapply(c("rec", "fai"), function(x){
  tmp <- estimates[estimates$rhs==x,]
  tmp$id_study <- tmp$country
  tmp$id_es <- 1:nrow(tmp)
  if(nrow(tmp) == 1) return(NULL)
  res <- tryCatch({rma.mv(tmp$bi, tmp$se^2, random = list(~ 1 | id_study, ~ 1 | id_es), data=tmp) }, error = function(e){rma(tmp$bi, tmp$se^2, data=tmp)})
  confints <- confint(res)
  tabres <- data.frame(Parameter = c(rownames(res$b), "Tau2b", "Tau2w"),
                       Estimate = c(fisherz2r(res$b), res$sigma2),
                       ci.lb = c(fisherz2r(res$ci.lb), confints[[1]]$random[1,2], confints[[2]]$random[1,2]),
                       ci.ub = c(fisherz2r(res$ci.ub), confints[[1]]$random[1,3], confints[[2]]$random[1,3]),
                       p = c(res$pval, NA, NA),
                       sig = c(c("", "*")[(res$pval < .05)+1], c("", "*")[(c(confints[[1]]$random[1,2], confints[[2]]$random[1,2])> 1e-4)+1]),
                       Model = "Overall")
  # By conservatism dimension
  res <- try(rma.mv(tmp$bi, tmp$se^2, random = list(~ 1 | id_study, ~ 1 | id_es), data=tmp, intercept = FALSE, mods = tmp[, c("social", "eco")]))
  if(inherits(res, "try-error")) return(tabres)
  confints <- confint(res)
  tabres2 <- data.frame(Parameter = c(rownames(res$b), "Tau2b", "Tau2w"),
                        Estimate = c(fisherz2r(res$b), res$sigma2),
                        ci.lb = c(fisherz2r(res$ci.lb), confints[[1]]$random[1,2], confints[[2]]$random[1,2]),
                        ci.ub = c(fisherz2r(res$ci.ub), confints[[1]]$random[1,3], confints[[2]]$random[1,3]),
                        p = c(res$pval, NA, NA),
                        sig = c(c("", "*")[(res$pval < .05)+1], c("", "*")[(c(confints[[1]]$random[1,2], confints[[2]]$random[1,2])> 1e-4)+1]),
                        Model = "Multigroup")
  if(tabres$Estimate[1] == tabres2$Estimate[1]) return(tabres)
  tabres <- rbind(tabres, tabres2)
  tabres$CI <- conf_int(lb = tabres$ci.lb, ub = tabres$ci.ub)
  tabres[c("ci.lb", "ci.ub")] <- NULL
  tabres$Domain <- x
  tabres
})
meta9 <- do.call(rbind, meta9)

saveRDS(bayesfactors, "bayesfactors.RData")
saveRDS(est_for_hyp, "est_for_hyp.RData")
saveRDS(res_list17, "res_list17.RData")
saveRDS(meta17, "meta17.RData")
saveRDS(meta8, "meta8.RData")
saveRDS(meta9, "meta9.RData")

@@

First, we provide an overview of the latent variable correlations for each country.
These are the model parameters evaluated using the informative hypothesis tests below:

```{r templatecortabs, include=FALSE}
res_list17 <- readRDS("res_list17.RData")
out = NULL
for (i in 1:length(res_list17)) {
  out = c(out, knit_expand('template_tabcor.rmd'))
}
```

`r paste(knit(text = out), collapse = '\n')`

Next, we examine evidence for the preregistered hypotheses:

```{r tabresults, results = "asis"}
bayesfactors <- readRDS("bayesfactors.RData")
est_for_hyp <- readRDS("est_for_hyp.RData")
interpret_bf <- function(bf){
  sapply(bf, function(bf){
    if(bf < 1/10) return("rejected")
    if(bf < 1/3) return("rejected")
    if(bf >= 1/3 & bf <= 3) return("inconclusive")
    if(bf > 3 & bf <= 10) return("supported")
  return("supported")
  })
}
invisible(lapply(1:length(bayesfactors), function(h){
  print({
    kbl(est_for_hyp[[h]], caption = paste0("Parameters used to test hypothesis ", h, ". Evidence in favor of the hypothesis: BF = ", formatC(bayesfactors[h], digits = 3, format = "f"), " (", interpret_bf(bayesfactors[h]), ")."), digits = 3) |>
  kable_styling(bootstrap_options = c("striped", "hover"))
})}))
```

@@

# Meta-analyses

Whereas the preregistered hypotheses test the hypothesis that *all* correlations between *all* moral domains and *all* conservatism scales will be > .1 in *all* countries,
we can also examine the *average* correlation between moral domains and conservatism scales across countries.
